Learned image compression

### 2023-03-14 paper/paper.tex

% Title.
% ------
\title{Learned image compression}
%
% Single address.
% ---------------
\name{Authors\\ Juha Ylikoski, Nardos Estifanos, Teemu Eerola \\Tampere University\thanks{Thanks to XYZ agency for funding.}}
\address{\{juha.ylikoski, nardos.estifanos, teemu.eerola\}@tuni.fi}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
The abstract should appear at the top of the left-hand column of text, about
0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
beginning of the main text.  The abstract should contain about 100 to 150
words, and should be identical to the abstract text submitted electronically
along with the paper cover sheet.  All manuscripts must be in English, printed
in black ink.
\end{abstract}
%
\begin{keywords}
AUTHORS CONTRIBUTION?
\end{keywords}
%
\section{Introduction} % Juha
\label{sec:intro}
With the rise of cloud services and mobile devices, the amount of stored digital media has grown rapidly. 
Large part of this data is stored images which take considerable amount of space.
Traditionally these images have been compressed or encoded to formats like jpeg or png which compress the images and usually lose some details (lossy compression).
With the rise of neural networks and machine learning there has been many attempts to achieve higher compression ratios and lose less details.
Many of these methods have achieved higher compression ratio with better perceived image quality and less visible artifacts but have been prohibitively expensive in terms of computational cost.

This work tries to replicate paper from He \textit{et al.}\cite{ELIC} which has introduced an efficient learned image compression method (ELIC) which fairs well in the benchmarks and is also reasonable in terms of computational cost.
The model is based on multiple convolutional neural networks which encode the image into latent space.
This latent representation is then passed into autoencoder which compresses it and is sent to the receiver. 
The autoencoder takes as parameters input from a model they call Space-Channel ConTeXt (SCCTX).
This model optimizes the encoding/decoding parameters of Gaussian encoder to minimize the redundancy in both channel dimension and in spatial dimension to further reduce the number of bits transferred.

>>>>

% Title.
% ------
\title{Learned image compression}
%
% Single address.
% ---------------
\name{Juha Ylikoski, Teemu Eerola, Nardos Estifanos}
\address{juha.ylikoski@tuni.fi, teemu.eerola@tuni.fi, nardos.estifanos@tuni.fi}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
The abstract should appear at the top of the left-hand column of text, about
0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
beginning of the main text.  The abstract should contain about 100 to 150
words, and should be identical to the abstract text submitted electronically
along with the paper cover sheet.  All manuscripts must be in English, printed
in black ink.
\end{abstract}
%
\begin{keywords}
Learned image compression
\end{keywords}
%

\setcounter{section}{-1}

\section{Authors' contributions}

\section{Introduction} % Juha
\label{sec:intro}
With the rise of cloud services and mobile devices, the amount of stored digital media has grown rapidly. 
Large part of this data is stored images which take considerable amount of space.
Traditionally these images have been compressed or encoded to formats like jpeg or png which compress the images and usually lose some details (lossy compression).
With the rise of neural networks and machine learning there has been many attempts to achieve higher compression ratios and lose less details.
Many of these methods have achieved higher compression ratio with better perceived image quality and less visible artifacts but have been prohibitively expensive in terms of computational cost.

This work tries to replicate paper ELIC: Efficient learned image compression with unevenly grouped space-channel contextual adaptive coding \cite{ELIC} which has introduced an efficient learned image compression method (ELIC) which fairs well in the benchmarks and is also reasonable in terms of computational cost.
The model is based on multiple convolutional neural networks which encode the image into latent space.
This latent representation is then passed into autoencoder which compresses it and is sent to the receiver. 
The autoencoder takes as parameters input from a model they call Space-Channel ConTeXt (SCCTX).
This model optimizes the encoding/decoding parameters of Gaussian encoder to minimize the redundancy in both channel dimension and in spatial dimension to further reduce the number of bits transferred.
